A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2022-10-26 Papers/Paper/manuscript.Rmd
fix footnote

A word can be unpredictable for a variety of reasons: it could be low frequency, semantically unexpected, the start of a low-frequency syntactic construction, or a word that disambiguates prior words to a less common parse. Many targeted effects of interest can thus be potentially accomodated theoretically as specific features that influence word predictability.[^Of course, not all effects can necessarily be reduced to word predictability effects, and effects that *cannot* be reduced to word predictability may be of particular theoretical interest. Candidates include, for example, memory-based effects [@lewis-etal:2006; @levy-fedorenko-gibson:2013jml], noisy-channel error identification [@levy-etal:2009pnas], and the magnitude of processing difficulty in garden-path resolution [@van-schijndel-linzen-2021:single-stage-models; @wilcoxTargetedAssessmentIncremental2021].] Thus incremental processing methods that are sensitive to predictability are useful for testing linguistic theories that make predictions about what words are unexpected.

>>>>

A word can be unpredictable for a variety of reasons: it could be low frequency, semantically unexpected, the start of a low-frequency syntactic construction, or a word that disambiguates prior words to a less common parse. Many targeted effects of interest can thus be potentially accommodated theoretically as specific features that influence word predictability. ^[Of course, not all effects can necessarily be reduced to word predictability effects, and effects that *cannot* be reduced to word predictability may be of particular theoretical interest. Candidates include, for example, memory-based effects [@lewis-etal:2006; @levy-fedorenko-gibson:2013jml], noisy-channel error identification [@levy-etal:2009pnas], and the magnitude of processing difficulty in garden-path resolution [@van-schijndel-linzen-2021:single-stage-models; @wilcoxTargetedAssessmentIncremental2021].] Thus incremental processing methods that are sensitive to predictability are useful for testing linguistic theories that make predictions about what words are unexpected.
